### 2010-02-27 byu_studies/poster.tex
Some more work on the poster.  Getting closer

\usepackage{times}
\usepackage{calc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage{multirow}
\usepackage{bm}

@@

\definecolor{lightblue}{cmyk}{.3,0,0,0.0}
\definecolor{lighterblue}{cmyk}{.2,0,0,0.0}
\definecolor{lightestblue}{cmyk}{.1,0,0,0.0}
\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=lighterblue,
  bgColorTwo=lightestblue,
  borderColor=reddishblue,
  headerColorOne=blue,
  headerColorTwo=reddishblue,
  headerFontColor=black,
  boxColorOne=lightblue,
  boxColorTwo=lighterblue,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=no,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=plain,
  background=shade-tb,
  %background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  Automatic Topic Discovery in 100 Years of General Conference Talks}
  % Authors
  {\sf %Sans Serif
  % Serif
  Matthew Gardner
  (mjg82@byu.edu)
  and
  Eric Ringger
  (ringger@cs.byu.edu)
  }
  % University logo
  {{\begin{minipage}{16em}
    \hfill
    %\includegraphics[height=5.5em]{logo}
  \end{minipage}}
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Background and Methodology}
  {name=methodology,column=0,below=contribution}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	Document clustering is the task of determining which documents are similar
	to each other in any given corpus.  The fundamental assumption made by
	clustering techniques is that there are several topics used in the corpus,
	and each document is generated by a single (unknown) topic.  Given a
	clustering model and a set of documents, statistical methods can be used to
	determine the best clustering of documents for that corpus.

	When documents frequently cover multiple topics, however, the performance
	of document clustering methods degenerates.  This is often the case with
	religious discourse, as talks frequently combine faith and repentance, or
	faith and tithing, making the talks seem similar in regards to their use of
	words describing faith, but different in the other topics they cover.  To
	solve this problem, Latent Dirichlet Allocation (LDA) was proposed.  LDA
	breaks the assumption of document clustering that each document is
	generated from a single topic, and instead assumes that each word in each
	document comes from a particular topic.  Thus documents can have multiple
	topics, creating a better model for many corpora of interest today.

	LDA can be used both to discover the topics that are spoken of throughout a
	corpus and to determine which documents in the corpus use which topics most
	frequently.  When documents have dates and authors associated with them,
	other interesting attributes of the corpus, such as the relative
	proportions of topics over time, can also be deduced.  We used LDA to
	automatically discover topics found in General Conference talks from
	1900--2005.  We obtained the talks from the internet site
	www.ldslibrary.org.  There is some noise in the data because of parsing
	error, but overall the quality is high.

>>>>

\usepackage{times}
\usepackage{calc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage{multirow}
\usepackage{bm}
\usepackage{psfrag}

@@

\definecolor{lightblue}{cmyk}{.3,0,0,0.0}
\definecolor{lighterblue}{cmyk}{.2,0,0,0.0}
\definecolor{lightestblue}{cmyk}{.1,0,0,0.0}
\begin{poster}{
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=lighterblue,
  bgColorTwo=lightestblue,
  borderColor=reddishblue,
  headerColorOne=blue,
  headerColorTwo=reddishblue,
  headerFontColor=black,
  boxColorOne=lightblue,
  boxColorTwo=lighterblue,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=no,
  headerborder=open,
  headerheight=0.08\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\Large\textsf, %Sans Serif
  boxshade=plain,
  background=shade-tb,
  %background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  Automatic Topic Discovery in 100 Years of General Conference Talks}
  % Authors
  {\sf %Sans Serif
  % Serif
  Matthew Gardner
  (mjg82@byu.edu)
  and
  Eric Ringger
  (ringger@cs.byu.edu)
  }
  % University logo
  {{\begin{minipage}{16em}
    \hfill
    \includegraphics[height=5.5em]{byunlp.eps}
  \end{minipage}}
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Topic Discovery with LDA}
  {name=lda,column=0,below=contribution}{

	  We automatically discover topics using Latent Dirichlet Allocation (LDA).
	  The LDA algorithm works as follows:
	  \begin{itemize}
		\item There is some number of topics in the corpus (we picked 100).
		\item Assume each word in each document comes from one topic.
		\item Use statistical relationships among words in the corpus to group 
		  the words into topics.
	  \end{itemize}

  }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{LDA Graphical Model}
  {name=methodology,column=0,below=lda}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	\begin{centering}
	  \psfrag{b}[C][C]{\huge$\beta$}
	  \psfrag{a}[C][C]{\huge$\alpha$}
	  \psfrag{t}[C][C]{\huge$\theta$}
	  \psfrag{f}[C][C]{\huge$\phi$}
	  \psfrag{w}[C][C]{\huge$w$}
	  \psfrag{z}[C][C]{\huge$z$}
	  \psfrag{N}[C][C]{\Large$N$}
	  \psfrag{M}[C][C]{\Large$M$}
	  \psfrag{K}[C][C]{\Large$K$}
	  \includegraphics[height=.82\linewidth]{lda_model.eps}
	  \begin{align*} 
		w_i|z_i,\phi^{(z_i)} &\sim \mathrm{Categorical}(\phi^{(z_i)}) \\
		\phi &\sim \mathrm{Dirichlet}(\beta) \\
		z_i|\theta^{(d_i)} &\sim \mathrm{Categorical}(\theta^{(d_i)}) \\ 
		\theta &\sim \mathrm{Dirichlet}(\alpha) 
	  \end{align*}
	\end{centering}
